One-Particle Density Matrix Polarisation Susceptibility Tensors

### 2018-08-10 papers/1_dmatpol/submit/paper-submit.tex
Rederivation. Complex numbers checkup and revision.

Most of the efforts to theoretically treat extended molecular aggregates are rooted in energy\hyp{}based 
philosophy. However, in the past two decades there has been considerable interest in density\hyp{}based approaches
of a wider scope and aims.\cite{Yang.Lee.JCP.1995,
Mukamel.Berman.JCP.2003,
Piquemal.Cisneros.Reinhardt.Gresh.Darden.JCP.2006,
Elliott.Burke.Cohen.Wasserman.PhysRevA.2010,
Mandado.Hermida-Ramon.JCTC.2011,Sun.Chan.ACR.2016,Hedegard.Reiher.JCTC.2016} 
In particular, the importance of one\hyp{}electron densities in chemistry is well known and acknowledged 
in the community,\cite{Holas.March.PhysRevA.1991,Yang.PhysRevLett.1991,Yang.Lee.JCP.1995} 
though obtaining the accurate electron density distribution 
has been an unresolved issue for most of chemical systems in condensed phases. Given that fact, it would be 
incredibly insightful to establish a first\hyp{}principles connection between the one\hyp{}particle density 
and the perturbation in the environment through introduction of \emph{density matrix susceptibility} (DMS) tensors. 
The main postulate of the present work is that the associated change in the one\hyp{}particle density matrix, 
$\delta {\bf D}$, can be represented in a product form of the generalised perturbation susceptibility ${\bf B}_i$
and the environment\hyp{}induced perturbation on a molecule, $\delta {\bf P}_i$, evaluated at certain site $i$,
%
\begin{equation*} \label{e:initial-model}
  \delta {\bf D} \approx \sum_i^{\text{Sites}} {\bf B}_i
  \cdot  \delta {\bf P}_i \;.
\end{equation*}
%
While $\delta {\bf P}_i$ contains critical information about the actual distortion of the electronic cloud,
perturbation susceptibility is assumed to be a property of unperturbed molecule and is to be precomputed only once. 
Thus, such DMS could be adapted into an efficient effective one\hyp{}electron fragment potential which in principle, 
is applicable to an arbitrary level of theory, as long as the one\hyp{}particle densities are available by means of
quantum chemistry methods. It also means that such a technique would dramatically reduce costs of quantum chemistry 
calculations because the task of performing full computation on a molecular aggregate would reduce to much simpler
matrix operations.

@@

In the limit of a weak and spatially uniform electric field,
the polarisation\hyp{}induced density matrix change of any electronic state
or electronic transition is given by the following Taylor expansion:
%
\begin{equation}\label{e:dD-Taylor}
 \delta D_{\alpha\beta} = \frac{\partial D_{\alpha\beta}}{\partial {\bf F}}\Bigg|_{{\bf F}={\bf 0}}  \cdot {\bf F} 
   + \frac{1}{2} 
     \frac{\partial^2 D_{\alpha\beta}}{\partial {\bf F} \otimes \partial {\bf F}}\Bigg|_{{\bf F}={\bf 0}} : {\bf F} \otimes {\bf F}
   + \ldots 
\end{equation}
%
In the above expression, the density matrix susceptibilities 
are simply equal to the derivatives of the density matrix
with respect to electric field (up to a multiplicative constant).
In a general case, i.e., when electric field is relatively strong 
and non\hyp{}uniform, single\hyp{}centred expansions, like the one 
from Eq.~\eqref{e:dD-Taylor},
%although valid for an arbitrary level of theory in uniform fields,
are not sufficient enough to accurately describe the local polarisation
of electron density distribution.

@@

In the Hartree\hyp{}Fock theory,\cite{Roothaan.RevModPhys.1951} ${\bf D}$ is approximated as
%
\begin{equation}
 {\bf D} = {\bf C} \cdot {\bf C}^\dagger \;,
\end{equation}
%
where ${\bf C}$ describes the occupied molecular orbitals (MO's) as linear combinations
of AO's, referred here to as the LCAO-MO matrix.
${\bf D}$ is an idempotent matrix and if expressed in orthogonal basis the following holds
%
\begin{equation}
 {\bf D}^2 = {\bf D} \;.
\end{equation}
%
The change in the molecular orbitals can be parameterised as suggested by McWeeny\cite{McWeeny.RevModPhys.1960}
by defining the idempotency\hyp{}preserving variation
%
\begin{equation}
 \delta {\bf C} = {\BM\Delta} \cdot {\bf C}^{(0)} \;,
\end{equation}
%
where $\BM\Delta$ is a square non\hyp{}singular and non\hyp{}symmetric matrix.
McWeeny showed that
%
\begin{equation} \label{e:dmat-change.exact}
 \delta {\bf D} = -{\bf D}^{(0)} + \left[ {\bf D}^{(0)} + {\bf v} \right] \cdot
                                   \left[ {\bf 1} + {\bf v}^\dagger \cdot {\bf v} \right]^{-1} \cdot
                                   \left[ {\bf D}^{(0)} + {\bf v}^\dagger \right] \;,
\end{equation}
%
where the auxiliary vector ${\bf v}$ is defined as
%
\begin{equation}
 {\bf v} \equiv \left[ {\bf 1} - {\bf D}^{(0)} \right] \cdot {\BM\Delta} \cdot {\bf D}^{(0)}  \;.
\end{equation}
%
Expanding Eq.~\eqref{e:dmat-change.exact} in a Taylor series around ${\bf v}={\bf 0}$ and
truncating it at linear terms with respect to ${\BM\Delta}$ gives
%
\begin{subequations} 
 \begin{align}
 \delta {\bf D} &\cong \left[ {\bf 1} - {\bf D}^{(0)} \right] \cdot {\BM\Delta} \cdot {\bf D}^{(0)} + 
                        {\bf D}^{(0)} \cdot {\BM\Delta}^\dagger \cdot \left[ {\bf 1} - {\bf D}^{(0)} \right]  
 \label{e:dD-1} \\  &= 
  \delta {\bf C} \cdot {\bf C}^{(0)\dagger} + {\bf C}^{(0)} \cdot \delta {\bf C}^\dagger \nonumber \\
           &\qquad - {\bf D}^{(0)} \cdot \delta {\bf C} \cdot {\bf C}^{{(0)}\dagger} 
                   - {\bf C}^{(0)} \cdot \delta {\bf C}^\dagger \cdot {\bf D}^{(0)}  \;.
 \label{e:dD-2}
 \end{align}
\end{subequations}
%
The latter equality is true only if the basis set functions are orthogonal, i.e., 
${\bf C}^{(0)\dagger} \cdot {\bf C}^{(0)}={\bf 1}$,
which will be the case throughout the entire work, unless stated otherwise.
Substituting the result from Eq.~\eqref{e:dD-1}
into Eq.~\eqref{e:dmu-exact} leads to
%
\begin{multline} \label{e:dmu-4-exact.linear-approximation}
 \frac{1}{2} 
 \delta {\BM{\upmu}}
  \cong
   \Tr{ 
    \left[ 
         {\mathbb{M}} \cdot {\BM\Delta} \cdot {\bf D}^{(0)}  
    \right] }
%
  +\Tr{ 
    \left[ 
         {\mathbb{M}} \cdot {\bf D}^{(0)} \cdot {\BM\Delta}^{\dagger}
    \right] } \\
%
  -\Tr{ 
    \left[ 
         {\mathbb{M}} \cdot {\bf D}^{(0)} \cdot {\BM\Delta} \cdot {\bf D}^{(0)}
    \right] }
%
  -\Tr{ 
    \left[ 
         {\mathbb{M}} \cdot {\bf D}^{(0)} \cdot {\BM\Delta}^{\dagger} \cdot {\bf D}^{(0)}
    \right] } \;.
\end{multline}
%
It can be proven (see Appendix~\ref{a:orig-dep}) that such obtained
induced dipole moment is independent of the origin. 
This guarantees that the theory fulfils the total charge conservation requirement.
Therefore,
in the above result and also in later course of the paper the dipole origin will be omitted. 
%where the dipole origin was omitted for notational clarity.

Now, if the AO basis is orthogonal, Eq.~\eqref{e:dmu-4-exact.linear-approximation} can be simplified by realising that
%
\begin{equation}
 \frac{1}{2} 
 \delta {\BM{\upmu}}
  \cong
2 \Tr{ 
    \left[ 
         \widetilde{\mathbb{M}} \cdot \delta {\bf C}
   \right] }  
-
2 \Tr{ 
    \left[ 
         \widetilde{\mathbb{K}} \cdot \delta {\bf C}
   \right] } \;.
\end{equation}
%
Here we introduced the auxiliary tensors
%
\begin{subequations}
 \begin{align}
   \widetilde{\mathbb{M}}  &\equiv {\bf C}^{(0)\dagger} \cdot {\mathbb{M}}     \;,           \\
   \widetilde{\mathbb{K}}  &\equiv {\bf C}^{(0)\dagger} \cdot {\mathbb{M}} \cdot {\bf D}^{(0)} \;, \\
   \widetilde{\mathbb{L}}  &\equiv \widetilde{\mathbb{M}} - \widetilde{\mathbb{K}} \;
 \end{align}
\end{subequations}
%
to simplify the notation. Hence,
%
\begin{equation} \label{e:dmu-l-vector}
  \frac{1}{4} 
 \delta {\BM{\upmu}} %({\bf r}_0) 
   =
   \Tr{ 
    \left[ 
         \widetilde{\mathbb{L}} \cdot \delta {\bf C}
    \right] }
   %
   \equiv \sum_{i}^{\rm occ} \sum_\alpha {\bf l}_{i\alpha} \delta C_{\alpha i} \;,
\end{equation}
%
where the Cartesian vector
%
\begin{equation}\label{e:l-vector}
 {\bf l}_{i\alpha} \equiv \left[ \widetilde{\mathbb{M}} - \widetilde{\mathbb{K}} \right]_{i\alpha} 
      = \left[  {\bf C}^\dagger \cdot \mathbb{M} \cdot \left( {\bf 1} - {\bf D}^{(0)} \right) \right]_{i\alpha}
\end{equation}
%
and $i$ runs over occupied unperturbed MO's.
Note that the intermediate quantity $\widetilde{\mathbb{L}}$ contains the projector onto
the unoccupied MO space at the absence of the external electric field. It means that the
perturbed solution is constructed from the unperturbed virtual orbitals as well.
Although Eq.~\eqref{e:dmu-l-vector}
is exact up to first order in ${\BM\Delta}$, it cannot be inverted at this moment to obtain $\delta {\bf C}$
due to the presence of trace operation, unless the electric field is uniform.
Let the induced dipole moment be partitioned into separate contributions
from the occupied localised MO's (LMO's), i.e.,
%
\begin{equation} \label{e:dmu-part}
 \delta {\BM{\upmu}} = \sum_i^{\rm occ} \delta {\BM{\upmu}}_i \;,
\end{equation}
%
where
%
\begin{equation} \label{e:dmu-dpol}
 \delta {\BM{\upmu}}_i = {\BM{\alpha}}_i \cdot {\bf F}({\bf r}_i) \;.
\end{equation}
%
In Eq.~\eqref{e:dmu-dpol}, ${\BM{\alpha}}_i$ is the distributed dipole\hyp{}dipole polarisability tensor
associated with the $i$th LMO whereas ${\bf F}({\bf r}_i)$ 
is the electric field evaluated at the $i$th LMO charge centroid,
${\bf r}_i = \tbraket{\phi_i}{\hat{\bf r}}{\phi_i}$.
By inserting the above result into Eq.~\eqref{e:dmu-l-vector},
recasting the right hand side in a matrix form
and assuming real quantities,
one can separate the contributions coming from occupied MO's as
%
\begin{equation} \label{e:dmu-l-vector-mo-transform-X}
 \frac{1}{4} {\BM{\alpha}}_i \cdot {\bf F}({\bf r}_i) 
   =
   \delta {\bf c}_i^T \cdot {\bf L}_i \;.
\end{equation}
%
Note that now ${\bf L}_i$ is a matrix of dimension $n \times 3$ and $\delta{\bf c}_i$ is the $i$th column of the
change in the LCAO-MO matrix due to the polarisation process.
The solution for $\delta {\bf C}$ is
%
\begin{equation} \label{e:mu-ind.matrix.linear.solution}
  \delta {\bf c}_i^T = \frac{1}{4}
            {\bf F}({\bf r}_i)  \cdot {\BM{\alpha}}_i \cdot 
                    \left[ {\bf L}_i  \right]^{-1}_{\rm Left} \;,
\end{equation}
%
where $\left[ {\bf L}_i  \right]^{-1}_{\rm Left}$ is a left inverse
of ${\bf L}_i$ matrix,
%
\begin{equation} 
      \left[ {\bf L}_i  \right]^{-1}_{\rm Left}   \equiv
       \left[ {\bf L}_i^T \cdot {\bf L}_i \right]^{-1} \cdot {\bf L}_i^T   
\end{equation}
%
with the dimension of $3\times n$. Note that the right inverse of ${\bf L}_i$
does not exist because ${\bf L}_i \cdot {\bf L}_i^T$ is singular due to the fact that usually
$n > 3$.

>>>>

Most of the efforts to theoretically treat extended molecular aggregates are rooted in energy\hyp{}based 
philosophy. However, in the past two decades there has been considerable interest in density\hyp{}based approaches
of a wider scope and aims.\cite{Yang.Lee.JCP.1995,
Mukamel.Berman.JCP.2003,
Piquemal.Cisneros.Reinhardt.Gresh.Darden.JCP.2006,
Elliott.Burke.Cohen.Wasserman.PhysRevA.2010,
Mandado.Hermida-Ramon.JCTC.2011,Sun.Chan.ACR.2016,Hedegard.Reiher.JCTC.2016} 
In particular, the importance of one\hyp{}electron densities in chemistry is well known and acknowledged 
in the community,\cite{Holas.March.PhysRevA.1991,Yang.PhysRevLett.1991,Yang.Lee.JCP.1995} 
though obtaining the accurate electron density distribution 
has been an unresolved issue for most of chemical systems in condensed phases. Given that fact, it would be 
incredibly insightful to establish a first\hyp{}principles connection between the one\hyp{}particle density 
and the perturbation in the environment through introduction of \emph{density matrix susceptibility} (DMS) tensors. 
The main postulate of the present work is that the associated change in the one\hyp{}particle density matrix, 
$\delta {\bf D}$, can be represented in a product form of the generalised perturbation susceptibility ${\bf B}_i$
and the environment\hyp{}induced perturbation on a molecule, $\delta {\bf P}_i$, evaluated at certain site $i$,
%
\begin{equation*} \label{e:initial-model}
  \delta {\bf D} \approx \sum_i^{\text{Sites}} {\bf B}_i
  \cdot  \delta {\bf P}_i \;,
\end{equation*}
%
where the `$\cdot$' symbol denotes the inner tensor (dot) product.
While $\delta {\bf P}_i$ contains critical information about the actual distortion of the electronic cloud,
perturbation susceptibility is assumed to be a property of unperturbed molecule and is to be precomputed only once. 
Thus, such DMS could be adapted into an efficient effective one\hyp{}electron fragment potential which in principle, 
is applicable to an arbitrary level of theory, as long as the one\hyp{}particle densities are available by means of
quantum chemistry methods. It also means that such a technique would dramatically reduce costs of quantum chemistry 
calculations because the task of performing full computation on a molecular aggregate would reduce to much simpler
matrix operations.

@@

In the limit of a weak and spatially uniform electric field,
the polarisation\hyp{}induced density matrix change of any electronic state
or electronic transition is given by the following Taylor expansion:
%
\begin{equation}\label{e:dD-Taylor}
 \delta D_{\alpha\beta} = \frac{\partial D_{\alpha\beta}}{\partial {\bf F}}\Bigg|_{{\bf F}={\bf 0}}  \cdot {\bf F} 
   + \frac{1}{2} 
     \frac{\partial^2 D_{\alpha\beta}}{\partial {\bf F} \otimes \partial {\bf F}}\Bigg|_{{\bf F}={\bf 0}} : {\bf F} \otimes {\bf F}
   + \ldots 
\end{equation}
%
where the `$\otimes$' symbol denotes the outer tensor product.
In the above expression, the density matrix susceptibilities 
are simply equal to the derivatives of the density matrix
with respect to electric field (up to a multiplicative constant).
In a general case, i.e., when electric field is relatively strong 
and non\hyp{}uniform, single\hyp{}centred expansions, like the one 
from Eq.~\eqref{e:dD-Taylor},
%although valid for an arbitrary level of theory in uniform fields,
are not sufficient enough to accurately describe the local polarisation
of electron density distribution.

@@

In the Hartree\hyp{}Fock theory,\cite{Roothaan.RevModPhys.1951} ${\bf D}$ is approximated as
%
\begin{equation}
 {\bf D} = {\bf C} \cdot {\bf C}^\dagger \;,
\end{equation}
%
where ${\bf C}$ describes the occupied molecular orbitals (MO's) as linear combinations
of AO's, referred here to as the LCAO-MO matrix.
${\bf D}$ is an idempotent matrix and if expressed in orthogonal basis the following holds
%
\begin{equation}
 {\bf D}^2 = {\bf D} \;.
\end{equation}
%
The change in the molecular orbitals can be parameterised as suggested by McWeeny\cite{McWeeny.RevModPhys.1960}
by defining the idempotency\hyp{}preserving variation
%
\begin{equation}
 \delta {\bf C} = {\BM\Delta} \cdot {\bf C}^{(0)} \;,
\end{equation}
%
where $\BM\Delta$ is a square non\hyp{}singular and non\hyp{}symmetric matrix.
McWeeny showed that
%
\begin{equation} \label{e:dmat-change.exact}
 \delta {\bf D} = -{\bf D}^{(0)} + \left[ {\bf D}^{(0)} + {\bf v} \right] \cdot
                                   \left[ {\bf 1} + {\bf v}^\dagger \cdot {\bf v} \right]^{-1} \cdot
                                   \left[ {\bf D}^{(0)} + {\bf v}^\dagger \right] \;,
\end{equation}
%
where the auxiliary vector ${\bf v}$ is defined as
%
\begin{equation}
 {\bf v} \equiv \left[ {\bf 1} - {\bf D}^{(0)} \right] \cdot {\BM\Delta} \cdot {\bf D}^{(0)}  \;.
\end{equation}
%
Expanding Eq.~\eqref{e:dmat-change.exact} in a Taylor series around ${\bf v}={\bf 0}$ and
truncating it at linear terms with respect to ${\BM\Delta}$ gives
%
\begin{subequations} 
 \begin{align}
 \delta {\bf D} &\cong \left[ {\bf 1} - {\bf D}^{(0)} \right] \cdot {\BM\Delta} \cdot {\bf D}^{(0)} + 
                        {\bf D}^{(0)} \cdot {\BM\Delta}^\dagger \cdot \left[ {\bf 1} - {\bf D}^{(0)} \right]  
 \label{e:dD-1} \\  &= 
  \delta {\bf C} \cdot {\bf C}^{(0)\dagger} + {\bf C}^{(0)} \cdot \delta {\bf C}^\dagger \nonumber \\
           &\qquad - {\bf D}^{(0)} \cdot \delta {\bf C} \cdot {\bf C}^{{(0)}\dagger} 
                   - {\bf C}^{(0)} \cdot \delta {\bf C}^\dagger \cdot {\bf D}^{(0)}  \;.
 \label{e:dD-2}
 \end{align}
\end{subequations}
%
The latter equality is true only if the basis set functions are orthogonal, i.e., 
${\bf C}^{(0)\dagger} \cdot {\bf C}^{(0)}={\bf 1}$.
Such a condition is necessary in order to meet the charge conservation
requirement (see Appendix~\ref{a:orig-dep} for a detailed discussion).
Therefore orthogonality of AO's is assumed from that point, unless stated otherwise.
%Also, from this point onwards we assume that the molecular orbitals 
%and the transformation matrix $\BM \Delta$ are real.
Substituting the result from Eq.~\eqref{e:dD-1}
into Eq.~\eqref{e:dmu-exact} leads to
%
%\begin{multline} \label{e:dmu-4-exact.linear-approximation}
% \frac{1}{2} 
% \delta {\BM{\upmu}}({\bf r}_Q)
%  \cong
%   \Tr{ 
%    \left[ 
%         {\mathbb{M}} \cdot {\BM\Delta} \cdot {\bf D}^{(0)}  
%    \right] }
%%
%  +\Tr{ 
%    \left[ 
%         {\mathbb{M}} \cdot {\bf D}^{(0)} \cdot {\BM\Delta}^{\dagger}
%    \right] } \\
%%
%  -\Tr{ 
%    \left[ 
%         {\mathbb{M}} \cdot {\bf D}^{(0)} \cdot {\BM\Delta} \cdot {\bf D}^{(0)}
%    \right] }
%%
%  -\Tr{ 
%    \left[ 
%         {\mathbb{M}} \cdot {\bf D}^{(0)} \cdot {\BM\Delta}^{\dagger} \cdot {\bf D}^{(0)}
%    \right] } \;.
%\end{multline}
%
%This can be recast to
%
\begin{equation}\label{e:dmu-l-vector}
 \frac{1}{4} 
 \delta {\BM{\upmu}}({\bf r}_Q)
  \cong
  \Re \left\{ 
 \Tr{ 
    \left[ 
         \delta {\bf C} \cdot \mathbb{L}({\bf r}_Q)
   \right] }  
  \right\} \;,
\end{equation}
%
where the `$\Re$' symbol denotes the real part,
 and the intermediate quantity
%
\begin{equation} \label{e:L-projector}
 \mathbb{L}({\bf r}_Q) \equiv {\bf C}^{\dagger} \cdot \mathbb{M}({\bf r}_Q) \cdot \left( {\bf 1} - {\bf D}^{(0)} \right) \;.
\end{equation}
%
Note that $\mathbb{L}({\bf r}_Q)$ contains the projector onto
the unoccupied MO space at the absence of the external electric field. It means that the
perturbed solution is constructed from the unperturbed virtual orbitals as well.
Note also the similarity between Eq.~\eqref{e:L-projector} and Eq.~\eqref{e:dmu-exact}.
It can be proven (see Appendix~\ref{a:orig-dep}) that such obtained
induced dipole moment is independent of the origin. 
This guarantees that the theory fulfils the total charge conservation requirement.
Therefore, in later course of the paper the dipole origin will be omitted.

Although Eq.~\eqref{e:dmu-l-vector}
is exact up to first order in ${\BM\Delta}$, it cannot be inverted at this moment to obtain $\delta {\bf C}$.
If the orbitals are real, the analytic solution exists
provided that the electric field is uniform. In a more general case, i.e., when the electric field
is non\hyp{}uniform, the analytic solution cannot be found without further approximations.
Let the induced dipole moment be partitioned into separate contributions
from the occupied localised MO's (LMO's), i.e.,
%
\begin{equation} \label{e:dmu-part}
 \delta {\BM{\upmu}} = \sum_i^{\rm occ} \delta {\BM{\upmu}}_i \;,
\end{equation}
%
where the induced dipole moment associated with the $i$th LMO
is assumed to be linearly dependent on the local electric field, i.e.,
%
\begin{equation} \label{e:dmu-dpol}
 \delta {\BM{\upmu}}_i \approx {\BM{\alpha}}_i \cdot {\bf F}({\bf r}_i) \;.
\end{equation}
%
In Eq.~\eqref{e:dmu-dpol}, ${\BM{\alpha}}_i$ is the distributed dipole\hyp{}dipole polarisability tensor
associated with the $i$th LMO whereas ${\bf F}({\bf r}_i)$ 
is the electric field evaluated at the $i$th LMO charge centroid,
${\bf r}_i = \tbraket{\phi_i}{\hat{\bf r}}{\phi_i}$.
By inserting the above result into Eq.~\eqref{e:dmu-l-vector},
recasting the right hand side in a matrix form
and assuming real orbitals,
one can separate the contributions coming from the occupied MO's as
%
\begin{equation} \label{e:dmu-l-vector-mo-transform-X}
 \frac{1}{4} {\BM{\alpha}}_i \cdot {\bf F}({\bf r}_i) 
   =
   \delta {\bf c}_i^{\rm T} \cdot {\bf L}_i \;.
\end{equation}
%
Note that now ${\bf L}_i \equiv \left[ \mathbb{L} \right]_i$ 
is a real rectangular matrix of dimension $n \times 3$ and $\delta{\bf c}_i$ is the $i$th column of the
change in the LCAO-MO matrix due to the polarisation process.
The solution for $\delta {\bf C}$ is
%
\begin{equation} \label{e:mu-ind.matrix.linear.solution}
  \delta {\bf c}_i^{\rm T} = \frac{1}{4}
            {\bf F}({\bf r}_i)  \cdot {\BM{\alpha}}_i \cdot 
                    \left[ {\bf L}_i  \right]^{-1}_{\rm Left} \;,
\end{equation}
%
where $\left[ {\bf L}_i  \right]^{-1}_{\rm Left}$ is a left inverse
of ${\bf L}_i$ matrix,
%
\begin{equation} 
      \left[ {\bf L}_i  \right]^{-1}_{\rm Left}   \equiv
       \left[ {\bf L}_i^{\rm T} \cdot {\bf L}_i \right]^{-1} \cdot {\bf L}_i^{\rm T}   
\end{equation}
%
with the dimension of $3\times n$. Note that the right inverse of ${\bf L}_i$
does not exist because ${\bf L}_i \cdot {\bf L}_i^{\rm T}$ is singular due to the fact that usually
$n > 3$.
